Fluid-mechanical erosion creates anisotropic porous media

### 2022-06-01 docs/PhysicsPaper/StokesErosion.tex
NM

%-----------------------------------------------------------------------------------------------%
\subsection{Relationship to total drag}

The resistivity is directly related to the drag exerted by the bodies. Indeed, another way to express the Stokes equations is $\grad \cdot \stress = 0$ where $\stress = -p \bvec{I} + \mu \left( \grad \uu + \grad \uu^T \right)$ is the stress tensor. The divergence theorem gives
\begin{equation}
\label{divthm}
0 = \int_{\Omega} \grad \cdot \stress \, dV 
= \int_{\partial \Omega} \stress \cdot \nn \, ds
\end{equation}
for any domain $\Omega$.  Consider $\Omega$ to be inside $[-x_0, x_0] \times [-1, 1]$, where we will choose $x_0 > 1$ so that $\Omega$ includes the entire porous region.
The boundary integral on the right-hand-side of \eqref{divthm} has contributions from the boundaries of the erodable bodies $\gamma$ and from the outer boundary $\Gamma$, since $\partial \Omega = \gamma \cup \Gamma$. In particular, the total drag exerted by the erodable bodies is given by
\begin{equation}
\FD = -\int_{\gamma} \stress \cdot \nn \, ds
\end{equation}
which includes both pressure and viscous drag. The minus sign is due to the orientation of the normal vector. We will mostly be interested in the horizontal drag $\FD \cdot \ex$. \\

>>>>

%-----------------------------------------------------------------------------------------------%
\subsection{Total drag}

The permeability of the medium is directly related to the total drag exerted by the collection of bodies. The stress tensor associated with the Stokes equations \eqref{eqn:StokesEq} is given by $\stress = -p \bvec{I} + \mu \left( \grad \uu + \grad \uu^T \right)$, and an alternate expression of \eqref{eqn:StokesEq} is $\grad \cdot \stress = 0$. Integrating this form of the equations over an arbitrary domain $D$ and applying the divergence theorem gives
\begin{equation}
\label{divthm}
0 = \int_{D} \grad \cdot \stress \, dV 
= \int_{\partial D} \stress \cdot \nn \, ds
\end{equation}
Consider $D \subseteq [-x_0, x_0] \times [-1, 1]$ to be the subset consisting of the fluid region (i.e.~excluding solid bodies), where $x_0 \ge 1$ will be chosen to include the entire porous region plus some amount of the buffer region. The boundary $\partial D$ consist of $\gamma$, the solid boundaries of all of the bodies, as well as an outer boundary. The total drag exerted by all of the solid bodies is given by
\begin{equation}
\FD = -\int_{\gamma} \stress \cdot \nn \, ds
\end{equation}

\nick{Do I want plus or minus? I decided I want the drag exerted BY the bodies and so this should point to the left.}

Consider $\Omega$ to be inside $[-x_0, x_0] \times [-1, 1]$, where we will choose $x_0 > 1$ so that $\Omega$ includes the entire porous region.
The boundary integral on the right-hand-side of \eqref{divthm} has contributions from the boundaries of the erodable bodies $\gamma$ and from the outer boundary $\Gamma$, since $\partial \Omega = \gamma \cup \Gamma$. In particular, the total drag exerted by the erodable bodies is given by
\begin{equation}
\FD = -\int_{\gamma} \stress \cdot \nn \, ds
\end{equation}
which includes both pressure and viscous drag. The minus sign is due to the orientation of the normal vector. We will mostly be interested in the horizontal drag $\FD \cdot \ex$. \\
